---
title: "Random R Codes Part-1"
date: "2014-12-30"
output:
    html_document:
        toc: true
        theme: journal
        highlight: zenburn
--- 

R is now a large community. Today we have 6,139 R packages. I am planning here to jot down the code snippets  based on the newer packages (by following [table of available packages, sorted by date of publication](http://cran.r-project.org/web/packages/available_packages_by_date.html)). The chunk of the codes will be taken either from the Vignette or from the main package documentation pdf. I also like to include [stack overflow threads](http://stackoverflow.com/questions/tagged/r) if there are interesting questions. These interesting and easy-to-apply codes will be applied to different data sets to develop models and assumptions. Here's **Part 1**.

Five Packages used in Part 1. [Why 5? [Here's why.](http://petewarden.com)]

> countrycode, tableone, aRxiv, exams, gender

### countrycode

1. [Package pdf](http://cran.r-project.org/web/packages/countrycode/countrycode.pdf).
2. [Git Repository](https://github.com/vincentarelbundock/countrycode).
3. Last updated: 2014-12-29

```{r}
library(countrycode)

countrycode(232,"cown","country.name")
countrycode("United States","country.name","iso3c")
countrycode("DZA","iso3c","cowc")

cowcodes <- c("ALG","ALB","UKG","CAN","USA")
countrycode(cowcodes,"cowc","iso3c")

isocodes <- c(12,8,826,124,840)
var1     <- sample(1:500,5)
var2     <- sample(1:500,5)
df1      <- as.data.frame(cbind(cowcodes,var1))
df2      <- as.data.frame(cbind(isocodes,var2))
df1
df2
df1$iso3c   <- countrycode(df1$cowcodes, "cowc", "iso3c")
df2$iso3c   <- countrycode(df2$isocodes, "iso3n", "iso3c")
df3         <- merge(df1,df2,id="iso3c")
df3$country <- countrycode(df3$iso3c, "iso3c", "country.name")
df3
```

### tableone

1. [Package pdf](http://cran.r-project.org/web/packages/tableone/tableone.pdf).
2. [Vignette](http://cran.r-project.org/web/packages/tableone/vignettes/introduction.html).
3. [Git Repository](https://github.com/kaz-yos/tableone).
4. Last updated: 2014-12-29

```{r}
library(tableone)
library(survival)

## Simplest use case
head(pbc)
dim(pbc)
CreateTableOne(data = pbc)


library(vcd)
head(Arthritis)
dim(Arthritis)
CreateTableOne(data = Arthritis)

```
### aRxiv

1. [Package pdf](http://cran.r-project.org/web/packages/aRxiv/aRxiv.pdf).
2. [Vignette](http://cran.r-project.org/web/packages/aRxiv/vignettes/aRxiv.html).
3. [Git Repository](https://github.com/ropensci/aRxiv).
4. Last updated: 2014-12-29


```{r}
library(aRxiv)
deconv <- arxiv_search('au:"Dragan Slavkov Hajdukovic"', limit=21)
nrow(deconv)
deconv[, c('title', 'authors')]
```


### exams

1. [Package pdf](http://cran.r-project.org/web/packages/exams/exams.pdf).
2. [Vignette](http://cran.r-project.org/web/packages/exams/vignettes/exams.pdf).
3. Last updated: 2014-12-29

*Coding is not performed*

### gender

1. [Package pdf](http://cran.r-project.org/web/packages/gender/gender.pdf).
2. [Vignette](http://cran.r-project.org/web/packages/gender/vignettes/predicting-gender.html).
3. [Git Repository](https://github.com/ropensci/gender).
4. Last updated: 2014-12-29

```{r}
library(gender)
gender("Bobby")
gender("Nick")
gender("Lorretta")
gender("Bobby", method = "ipums", years = 1900)
gender("Bobby", method = "ssa", years = 1950)
gender("Bobby", method = "ssa", years = 2000)


```



--------------------
- Compiled by [Subasish Das](http://subasish.tumblr.com)